Time for a rethink: time sub-sampling methods in disparity-through-time analyses

### 2018-02-05 manuscript/time-slice.tex
Add subsampling to keywords
Edit fig 2 legend

\runninghead{Time sub-samples in disparity-through-time analyses}
\keywords{time bin, time-slice, disparity} 
% up to 6

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/fig-dtt-epoch.pdf}
    \caption[Relative disparity-through-time.]
    {Relative disparity-through-time. Median bootstrapped disparities were calculated using time binning and time-slicing approaches. 
    Pink points represent time binning methods, blue points are time-slices with a punctuated model of evolution (`proximity' method), and green points are time-slices with a gradual model of evolution (`gradual splits' method).
    Relative disparities (median bootstrapped disparity divided by the maximum median bootstrapped disparity for a dataset and analysis method) are presented so they can be compared across datasets/methods. 
    Stratigraphy uses unequal time bins or non-equidistant time-slices, where the width of the bin, or the interval between slices, is equivalent to stratigraphic epochs. 
    Duration uses equal time bins or equidistant time-slices, where the width of the bin, or the interval between slices, is the average duration of stratigraphic epochs in the time frame of the dataset. 
    Number uses equal time bins or equidistant time-slices, where the number of bins, or the number of slices, is the average number of stratigraphic epochs in the time frame of the dataset. 
    In all cases, time bin disparities are plotted at the midpoint of the bin, and error bars represent the 95\% confidence intervals around the bootstrapped median disparity.
    The four dataset names are on the first plot for each dataset (see Table \ref{table:datasets} for details).
    Results for stratigraphic stages, and for other time-slicing methods, are in the Supporting Information Appendix S2: Figures A1-A2.}
    \label{figure:dtt1}
\end{figure}

>>>>

\runninghead{Time sub-samples in disparity-through-time analyses}
\keywords{time bin, time-slice, disparity, sub-sampling} 
% up to 6

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/fig-dtt-epoch.pdf}
    \caption[Relative disparity-through-time.]
    {Relative disparity-through-time. Median bootstrapped disparities were calculated using time binning and time-slicing approaches. 
    Green points represent time binning methods, purple points are time-slices with a punctuated model of evolution (`proximity' method), and blue points are time-slices with a gradual model of evolution (`gradual splits' method).
    Relative disparities (median bootstrapped disparity divided by the maximum median bootstrapped disparity for a dataset and analysis method) are presented so they can be compared across datasets/methods. 
    Stratigraphy uses unequal time bins or non-equidistant time-slices, where the width of the bin, or the interval between slices, is equivalent to stratigraphic epochs. 
    Duration uses equal time bins or equidistant time-slices, where the width of the bin, or the interval between slices, is the average duration of stratigraphic epochs in the time frame of the dataset. 
    Number uses equal time bins or equidistant time-slices, where the number of bins, or the number of slices, is the average number of stratigraphic epochs in the time frame of the dataset. 
    In all cases, time bin disparities are plotted at the midpoint of the bin, and error bars represent the 95\% confidence intervals around the bootstrapped median disparity.
    The four dataset names are on the first plot for each dataset (see Table \ref{table:datasets} for details).
    Results for stratigraphic stages, and for other time-slicing methods, are in the Supporting Information Appendix S2: Figures A1-A2.}
    \label{figure:dtt1}
\end{figure}
